Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-07-29 summary.Rmd
still working on proof for theorem 5

$$\max\limits_{i, j} ||(\hat{v}^{(n)}_i)^\top \hat{v}_j^{(n)}|| = O_P\bigg( \frac{(\log n)^c}{n}\bigg)$$

@@

**Theorem 5**. Let $\lambda^{(kl)}_{n_k} \sim F_{n_k}$ for $k, l = 1, ..., K$, 
and let $\{\hat{\lambda}^{(kl)}_{n_k}\}_K$ be the set of estimates computed by 
Algorithm 4. 
Then ... ***TODO***

@@

* $K = 2$
* Mixture parameter $\alpha = .5$
* $\lambda^{(kk)} \stackrel{indep}{\sim} Beta(2, 1)$
* $\lambda^{(kl)} \stackrel{indep}{\sim} Beta(1, 2)$ for $k \neq l$

>>>>

$$\max\limits_{i, j} ||(\hat{v}^{(n)}_i)^\top \hat{v}_j^{(n)}|| = O_P\bigg( \frac{(\log n)^c}{n \sqrt{\rho_n}}\bigg)$$
where $\lim\limits_{n \to 0} \rho_n = 0$ is a sparsity parameter introduced 
by \citet{307cbeb9b1be48299388437423d94bf1}. More precisely, 
$\rho_n o(\log n / \sqrt{n})$.

@@

**Theorem 5**. Under assumptions 1-6 as laid out by \citet{307cbeb9b1be48299388437423d94bf1},

$$\sqrt{\frac{1}{n K} \sum_{k, l = 1}^K 
||\hat{\lambda}^{(kl)} - \lambda^{(kl)}||^2} 
\stackrel{P}{\to} 0$$

*Proof*. ***TODO***

@@

* $K = 2$
* Mixture parameter $\alpha = .5$
* $\lambda^{(kk)} \stackrel{iid}{\sim} Beta(2, 1)$
* $\lambda^{(kl)} \stackrel{iid}{\sim} Beta(1, 2)$ for $k \neq l$
